Welcome Home --- Now Vote!\thanks{The author thanks Jacob Faber, Jeff Manza, Myrna Pérez, Ariel White, and Peter Miller for their comments on this project. All errors are my responsibility.}

### 2020-10-28 markdown/part2/table_embed.Rmd
ssq abstract

---
title: "Welcome Home --- Now Vote!"
subtitle: "Voting Rights Restoration and Post-Supervision Participation"
thanks: The author thanks Jacob Faber, Jeff Manza, Myrna Pérez, Ariel White, and Peter Miller for their comments on this project. All errors are my responsibility.
author: Kevin Morris^[Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (kevin.morris@nyu.edu)]
institute: "Brennan Center for Justice"
date: |
  `r format(Sys.time(), '%B %d, %Y')`
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
    keep_tex: true
bibliography: "../welcome_home_vote.bib"
link-citations: yes
fontsize: 12pt
fontface: Times New Roman
header-includes:
    - \usepackage{rotating}
    - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
    - \usepackage{setspace}
    - \usepackage{lineno}
    - \linenumbers
abstract: |
  This paper presents causal estimates of the effect of voting rights restoration prior to discharge from parole on post-supervision participation. In 2018, New York State began restoring voting rights to individuals on parole, after previously restoring voting rights only at the completion of parole. By leveraging randomness in parole discharge date, I interrogate whether restoring voting rights to formerly incarcerated individuals while still on parole increases their post-supervision propensity to register and cast a ballot. I demonstrate that in-person rights restoration prior to parole discharge significantly increased participation, but this group-level effect masks racially heterogeneous effects. Although rights restoration prior to parole discharge increased turnout by non-Black individuals by 1.4 percentage points, the treatment effect was substantially smaller for Black individuals. This raises important questions about how members of different communities can be brought back into our democratic processes.
---
<!-- --- -->
<!-- title: "Neighborhoods and Felony Disenfranchisement: The Case of New York City" -->
<!-- author: "Kevin Morris" -->
<!-- date: "`r format(Sys.time(), '%B %d, %Y')`" -->
<!-- output: word_document -->
<!-- bibliography: "../research/citations.bib" -->
<!-- link-citations: yes -->
<!-- always_allow_html: yes -->
<!-- --- -->
\pagenumbering{gobble}
\pagebreak
\doublespacing
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "../..", dev = "cairo_pdf")
library(systemfit)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(data.table)
library(stargazer)
loadfonts()
```
\pagenumbering{arabic}
# Introduction {-}

@@

TABLE 1 ABOUT HERE

@@

TABLE 2 ABOUT HERE

@@

TABLE 3 ABOUT HERE

@@

TABLE 4 ABOUT HERE

@@

TABLE 5 ABOUT HERE

@@

FIGURE 1 ABOUT HERE

@@

TABLE 6 ABOUT HERE

@@

\newpage
# References {-}
<div id="refs"></div>

\newpage

```
```{r logit-reg-chunk-short, echo = F, results = "hide", message = F, warning = F}
load("temp/short_term_to.rdata")

```
\input{"../../temp/table3.tex"}
```{r rd-demo-chunk, echo = F, warning = F}
t <- readRDS("./temp/demos_rd_time.rds")
colnames(t) <- c("Variable", "Control", "ITT", "p-value")
j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:demo-rd) Demographics of Control and ITT Groups", linesep = "",
                  align = c("l", "c", "c"), "latex") %>% 
  kable_styling(latex_options = c("HOLD_position"),
                full_width = F)

write.table(j, "./temp/table_whatever2.tex", quote = F, col.names = F,
            row.names = F)
```
\input{"../../temp/table_whatever2.tex"}
```{r logit-reg-chunk, echo = F, results = "hide", message = F, warning = F}
load("./temp/individual_turnout_18_itt.rdata")
load("./temp/individual_turnout_16.rdata")

```
\input{"../../temp/table4.tex"}
```{r rd-dmeans, echo = F, warning = F}
k <- readRDS("./temp/means_diff_black.rds") %>% 
  select(-Statistic)
j <- knitr::kable(k, booktabs = T, caption = "(\\#tab:re) Turnout and Registration by Treatment Group, Race", linesep = "",
                  align = c("l", "c", "c", "c")) %>% 
  kable_styling(latex_options = c("HOLD_position"),
                full_width = F) %>% 
  group_rows(start_row = 1,
             end_row = 2,
             group_label = "Turnout") %>% 
  group_rows(start_row = 3,
             end_row = 4,
             group_label = "Registration")

write.table(j, "./temp/table_whatever3.tex", quote = F, col.names = F,
            row.names = F)
```
\input{"../../temp/table_whatever3.tex"}
```{r iv-reg-chunk, echo = F, results = "hide", message = F, warning = F}
load("temp/iv_individual_turnout_18.rdata")

\newpage
```{r sensitivity, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 6, fig.cap = "\\label{fig:sens}Estimated Treatment Effect by Window Size", fig.pos = "H", fig.align = "center"}
j <- readRDS("./temp/reestimates.rds")
print(j)
```

>>>>

---
title: "Welcome Home --- Now Vote!"
subtitle: "Voting Rights Restoration and Post-Supervision Participation"
thanks: The author thanks Jacob Faber, Jeff Manza, Myrna Pérez, Ariel White, and Peter Miller for their comments on this project. All errors are my responsibility.
author: Kevin Morris^[Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (kevin.morris@nyu.edu)]
institute: "Brennan Center for Justice"
date: |
  `r format(Sys.time(), '%B %d, %Y')`
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
    keep_tex: true
bibliography: "../welcome_home_vote.bib"
link-citations: yes
fontsize: 12pt
fontface: Times New Roman
header-includes:
    - \usepackage{rotating}
    - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
    - \usepackage{setspace}
    - \usepackage{lineno}
    - \linenumbers
abstract: |
  Objective: Past research demonstrates that formerly incarcerated individuals turn out at very low rates. Executive Order 181 in New York State allows us to test whether restoring voting rights at an in-person meeting while an individual is still on parole can increase their post-supervision registration and turnout.

  Methods: By linking administrative parole records with the registered voter file I estimate individual-level turnout. I use an interrupted time series and two-stage least squares approach to estimate the causal effect of Executive Order 181 on post-supervision participation.

  Results: I find that Executive Order 181 increased post-supervision registration and turnout for individuals discharged from parole as a whole; these results, however, mask racial heterogeneity. Although the participation of non-Black individuals increased substantially, the treatment effect for Black individuals was either much smaller or nonexistent.

  Conclusion: State policy can meaningfully increase the political participation of individuals even after they are no longer on parole. However, at least in the case of New York State, rights restoration prior to parole discharge appears less effective for Black individuals, who make up roughly 40 percent of the formerly incarcerated population.
---
<!-- --- -->
<!-- title: "Neighborhoods and Felony Disenfranchisement: The Case of New York City" -->
<!-- author: "Kevin Morris" -->
<!-- date: "`r format(Sys.time(), '%B %d, %Y')`" -->
<!-- output: word_document -->
<!-- bibliography: "../research/citations.bib" -->
<!-- link-citations: yes -->
<!-- always_allow_html: yes -->
<!-- --- -->
\pagenumbering{gobble}
\pagebreak
\doublespacing
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "../..", dev = "cairo_pdf")
library(systemfit)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(data.table)
library(stargazer)
loadfonts()
```
\pagenumbering{arabic}
# Introduction {-}

@@

```
\end{singlespace}

@@

\begin{singlespace}
```{r logit-reg-chunk-short, echo = F, results = "hide", message = F, warning = F}
load("temp/short_term_to.rdata")

```
\input{"../../temp/table3.tex"}
\end{singlespace}

@@

\begin{singlespace}
```{r rd-demo-chunk, echo = F, warning = F}
t <- readRDS("./temp/demos_rd_time.rds")
colnames(t) <- c("Variable", "Control", "ITT", "p-value")
j <- knitr::kable(t, booktabs = T, caption = "(\\#tab:demo-rd) Demographics of Control and ITT Groups", linesep = "",
                  align = c("l", "c", "c"), "latex") %>% 
  kable_styling(latex_options = c("HOLD_position"),
                full_width = F)

write.table(j, "./temp/table_whatever2.tex", quote = F, col.names = F,
            row.names = F)
```
\input{"../../temp/table_whatever2.tex"}
\end{singlespace}

@@

\begin{singlespace}
```{r logit-reg-chunk, echo = F, results = "hide", message = F, warning = F}
load("./temp/individual_turnout_18_itt.rdata")
load("./temp/individual_turnout_16.rdata")

```
\input{"../../temp/table4.tex"}
\end{singlespace}

@@

\begin{singlespace}
```{r rd-dmeans, echo = F, warning = F}
k <- readRDS("./temp/means_diff_black.rds") %>% 
  select(-Statistic)
j <- knitr::kable(k, booktabs = T, caption = "(\\#tab:re) Turnout and Registration by Treatment Group, Race", linesep = "",
                  align = c("l", "c", "c", "c")) %>% 
  kable_styling(latex_options = c("HOLD_position"),
                full_width = F) %>% 
  group_rows(start_row = 1,
             end_row = 2,
             group_label = "Turnout") %>% 
  group_rows(start_row = 3,
             end_row = 4,
             group_label = "Registration")

write.table(j, "./temp/table_whatever3.tex", quote = F, col.names = F,
            row.names = F)
```
\input{"../../temp/table_whatever3.tex"}
\end{singlespace}

@@

```{r sensitivity, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 6, fig.cap = "\\label{fig:sens}Estimated Treatment Effect by Window Size", fig.pos = "H", fig.align = "center"}
j <- readRDS("./temp/reestimates.rds")
print(j)
```

@@

\begin{singlespace}
```{r iv-reg-chunk, echo = F, results = "hide", message = F, warning = F}
load("temp/iv_individual_turnout_18.rdata")

@@

\newpage
# References {-}

### 2020-10-28 markdown/part2/table_embed.tex
ssq abstract

\title{Welcome Home --- Now Vote!\thanks{The author thanks Jacob Faber, Jeff Manza, Myrna Pérez, Ariel White, and Peter Miller for their comments on this project. All errors are my responsibility.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Voting Rights Restoration and Post-Supervision Participation}
\author{Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
\date{October 27, 2020}

\begin{document}
\maketitle
\begin{abstract}
This paper presents causal estimates of the effect of voting rights restoration prior to discharge from parole on post-supervision participation. In 2018, New York State began restoring voting rights to individuals on parole, after previously restoring voting rights only at the completion of parole. By leveraging randomness in parole discharge date, I interrogate whether restoring voting rights to formerly incarcerated individuals while still on parole increases their post-supervision propensity to register and cast a ballot. I demonstrate that in-person rights restoration prior to parole discharge significantly increased participation, but this group-level effect masks racially heterogeneous effects. Although rights restoration prior to parole discharge increased turnout by non-Black individuals by 1.4 percentage points, the treatment effect was substantially smaller for Black individuals. This raises important questions about how members of different communities can be brought back into our democratic processes.
\end{abstract}

@@

TABLE 1 ABOUT HERE

@@

TABLE 2 ABOUT HERE

@@

TABLE 3 ABOUT HERE

@@

TABLE 4 ABOUT HERE

@@

TABLE 5 ABOUT HERE

@@

FIGURE 1 ABOUT HERE

@@

TABLE 6 ABOUT HERE

@@

\caption{\label{tab:shift-dobs-chunk}\label{tab:change-dobs} Results of Shifting Birthdates}
\centering
\begin{tabular}[t]{cc}
\toprule
Group & \makecell[l]{Number of Matches Between\\DOCCS and Voter File Records}\\
\midrule
Actual Birthdate & 69,644\\
Birthdate + 35 Days & 502\\
Birthdate - 35 Days & 426\\
\bottomrule
\end{tabular}
\end{table}

\input{"../../temp/table3.tex"}

\input{"../../temp/table_whatever2.tex"}

\input{"../../temp/table4.tex"}

\input{"../../temp/table_whatever3.tex"}

\newpage
\begin{figure}[H]

{\centering \includegraphics{rewrite_files/figure-latex/sensitivity-1}

>>>>

\title{Welcome Home --- Now Vote!\thanks{The author thanks Jacob Faber, Jeff Manza, Myrna Pérez, Ariel White, and Peter Miller for their comments on this project. All errors are my responsibility.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Voting Rights Restoration and Post-Supervision Participation}
\author{Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
\date{October 28, 2020}

\begin{document}
\maketitle
\begin{abstract}
Objective: Past research demonstrates that formerly incarcerated individuals turn out at very low rates. Executive Order 181 in New York State allows us to test whether restoring voting rights at an in-person meeting while an individual is still on parole can increase their post-supervision registration and turnout.

Methods: By linking administrative parole records with the registered voter file I estimate individual-level turnout. I use an interrupted time series and two-stage least squares approach to estimate the causal effect of Executive Order 181 on post-supervision participation.

Results: I find that Executive Order 181 increased post-supervision registration and turnout for individuals discharged from parole as a whole; these results, however, mask racial heterogeneity. Although the participation of non-Black individuals increased substantially, the treatment effect for Black individuals was either much smaller or nonexistent.

Conclusion: State policy can meaningfully increase the political participation of individuals even after they are no longer on parole. However, at least in the case of New York State, rights restoration prior to parole discharge appears less effective for Black individuals, who make up roughly 40 percent of the formerly incarcerated population.
\end{abstract}

@@

\caption{\label{tab:shift-dobs-chunk}\label{tab:change-dobs} Results of Shifting Birthdates}
\centering
\begin{tabular}[t]{cc}
\toprule
Group & \makecell[l]{Number of Matches Between\\DOCCS and Voter File Records}\\
\midrule
Actual Birthdate & 69,644\\
Birthdate + 35 Days & 502\\
Birthdate - 35 Days & 426\\
\bottomrule
\end{tabular}
\end{table}
\end{singlespace}

@@

\begin{singlespace}

\input{"../../temp/table3.tex"}
\end{singlespace}

@@

\begin{singlespace}

\input{"../../temp/table_whatever2.tex"}
\end{singlespace}

@@

\begin{singlespace}

\input{"../../temp/table4.tex"}
\end{singlespace}

@@

\begin{singlespace}

\input{"../../temp/table_whatever3.tex"}
\end{singlespace}

@@

\begin{figure}[H]

{\centering \includegraphics{table_embed_files/figure-latex/sensitivity-1}

@@

\begin{singlespace}

@@
